---
title: "my_snippets"
author: "rccline"
date: "2/28/2021"
output: html_document
---

snippet my_polynomial
	plot(${1:myxcol}, ${2:myycol}, main="Polynomial Regression", las=1)
	model1 <- lm(${2:myycol} ~ ${1:myxcol}, data=${3:mydf})
	summary(model1)
		Use Residual Plots to check linearity
	model2 <- lm(${2:myycol} ~ ${1:myxcol} + I(${1:myxcol}^2), data=${3:mydf} )
	summary(model2)
		Use "Poly" command for polynomial

	model_poly <- lm(${2:myycol} ~ poly(${1:myxcol}, degree=2, raw=T), data=model)
	summary(model_poly)
		Add line
	lines(smooth.spline(${1:myxcol}, predict(model_poly)), col="blue", lwd=3)
		Partial F Test to compare models:
	anova(model1, model_poly)
		Fit a model with X^3
	model3 <- lm(${2:myycol} ~ ${1:myxcol} + I(${1:myxcol^2) + I(${1:myxcol}^3), data=${3:mydf})
	lines(smooth.spline(${1:myxcol}, predict(model3)), col="green", lwd=3, lty=3)
	legend(46, 15, legend = c("model1: linear", "model2: poly x^2", "model3: poly x^3"), col=c("red", "blue", "green"), lty=c(1,1,3), lwd=3, bty="n", cex=0.9)

snippet my_show_text
	library(showtext) 
	font_add_google("Montserrat")
	# font_add_google("Roboto Mono", "Roboto Mono")
	# Automatically use showtext to render text
	showtext_auto()

snippet my_date_format
	mutate(Dated= format(LseDate, "%B %d, %Y"))  
	YAML date: "Printed `r format(Sys.time(), '%a, %B %d, %Y')`"
	
snippet my_page_break
	<div style="page-break-after: always;"></div>
	
snippet my_underscores_to_spaces  
	names(sample_data_refi) <- gsub("_", " ", names(sample_data_refi))

snippet my_randomNos
	set.seed(2020)
	runif(1,0,10) # Random Nos No of digits, interval between 0 and 10 (n, min, max) 
	rnorm(n, mean= 0, sd = 1)
	
	
snippet my_recode
	${1:my_df$var1} $ ${2:my_var1}  <- recode(${1:my_df} $ ${2:my_var1},
		"PA" = "PR",
		"SI" = "PR")

snippet my_replace
	my_df$dt_pa2 = my_df$dt_pa  
	my_df
	my_df$dt_pa2[is.na(my_df$dt_pa2)] = "2020-10-4"
	summary(my_df)

snippet my_case_when
	${1:my_df} %>% 
		mutate(producer = case_when(is.na(dt_prod) ~  0,
																!is.na(dt_prod) ~ 1))
																
snippet my_NA's
${1:my_df} %>% 
	select(${2:my_var1}) %>% 
	summarise(NA_per_row = sum(is.na(.)), Not_NA= sum(!is.na(.)))
	
snippet  my_NA_impute
		"https://datascienceplus.com/imputing-missing-data-with-r-mice-package/"
		impute <- mice(${1:my_df}[, 2:9], m=5, seed = 123)
		print(impute)
	
snippet my_NA_pct
		library(mice)
		library(VIM)
		"https://datascienceplus.com/imputing-missing-data-with-r-mice-package/"
		aggr_plot <- aggr(${1:my_df}, col=c("navyblue","red"), numbers=TRUE, sortVars=TRUE,
		labels=names(${1:my_df}), cex.axis=0.7, gap=3, ylab=c("Histogram of missing data","Pattern"))
		md.pattern(${1:my_df})
		${1:my_df}$imp$my_var1
		md.pairs(${1:my_df})
		marginplot(${$:my_df[ c("${2:my_var1}","${3:my_var2}")])
		densityplot(${1:my_df})
		pctNA <- function(x) {sum(is.na(x))/length(x)*100}
		apply(${1:my_df}, 2, pctNA)
		

snippet my_decade
	decade = round(year/10)*10)
	decade = year %/% 10 * 10


snippet my_custom_barchart	#
	library(ggplot2)
	library(scales)
	ggplot(${1:my_df}, aes(x=${2:myxcol}, y=${3:myycol})) + 
	geom_col(color = "black", fill="#0072B2") +
	theme_minimal() +
	theme(panel.border = element_blank(), panel.grid.major = element_blank(),
				panel.grid.minor = element_blank(), axis.line = element_line(colour = "gray"),
				plot.title = element_text(hjust = 0.5),
				plot.subtitle = element_text(hjust = 0.5)
	) +
	scale_y_continuous(label = comma) + 
	xlab("") +
	ylab("") +
	geom_text(aes(label=scales::dollar(${2:myycol})), vjust=1.5, colour="white", position=position_dodge(.9), size=5) +
	ggtitle("${4:mytitle}", subtitle = "${5:mysubtitle}") 
	
snippet my_boxplot_outliers
	dat <- ggplot2::${1:mydf}
	summary(${2:myvar})
		ggplot(${1:mydf}) +
		aes(x=${2:myvar})+
		geom_histogram(bins = 30L, fill = "#0c4c8a")+  # Bins ~ Square root of the no of obs.
		theme_minimal()    
	ggplot(${1:mydf})+
		aes(x="", y= ${2:myxvar})+
		geom_boxplot(fill="#0c4c8a")+
		theme_minimal()
	Extract_Outliers
		out <- boxplot.stats(${2:myvar})$out
	Extract_Row_nos
		out_ind <- which(${2:myvar} %in% c(out))
	boxplot(${2:myvar},
		ylab="${3:myvarname},
		main = "Boxplot of highway miles per gallon")
		mtext(paste("Outliers: ", paste(out, collapse = ",")), side=1)
	All observations that lie outside of 2.5 and 97.5 percentile are potential outliers.
	lower_bound <- quantile(${2:myvar}, 0.025)
	upper_bound <- quantile(${2:myvar}, 0.975)
	outlier_ind <- which(${2:myvar} < lower_bound | ${2:myvar} > upper_bound)  
	
snippet my_ggplot_line 
	ggplot2::${1:mydf} %>%
		group_by(year = 10 * (year %/% 10)) %>% 
		summarise(died= mean(died),
		success = mean(success))  %>% 
			pivot_longer(died:success, names_to = "outcome", values_to = "percent") %>% 
		ggplot(aes(year, percent, color= outcome)) +
		geom_line(alpha=0.7, size=1.5) +
		scale_y_continuous(labels = scales::percent_format())

snippet my_geom_bar_dodge
	library(babynames)
	ggplot(babynames, aes(year %/% 10*10, fill=sex)) +
	geom_bar(
		stat="count",
		position="dodge"
	)

snippet my_corr
		library(tidyverse)
		dat <- ${1:mydf} %>%
		select(${2:myvar1}, ${3:myvar2})
			# Pearson correlation between 2 variables
			# quantitative continuous variables
	cor(${2:myvar1}, ${3:myvar2})
			# correlation for all variables
	round(cor(${1:mydf}),
	digits = 2 # rounded to 2 decimals
	)
		# Pearson product-moment correlation test of two vars
		# alternative hypothesis: true correlation is not equal to 0
		test <- cor.test(${2:myvar1}, ${3:myvar2})
		test
			# improved correlation matrix
	library(corrplot)
	corrplot(cor(${1:mydf}),
		method = "number",
		type = "upper" # show only upper side
	)
	
snippet my_corr_p_test
	# correlation p-tests for whole dataset
	library(Hmisc)
	res <- rcorr(as.matrix(${1:mydf})) # rcorr() accepts matrices only
		# display p-values (rounded to 3 decimals)
		# round(res$P, 3)   # var= res dollar  sign P
		
snippet my_correllogram
	library(correlation)
	correlation::correlation(${1:mydf},
		include_factors = TRUE, method = "auto"
	)
		#corrplot_function
	corrplot2 <- function(data,
		method = "pearson",
		sig.level = 0.05,
		order = "original",
		diag = FALSE,
		type = "upper",
		tl.srt = 90,
		number.font = 1,
		number.cex = 1,
		mar = c(0, 0, 0, 0)) {
	library(corrplot)
	data_incomplete <- data
	data <- data[complete.cases(data), ]
	mat <- cor(data, method = method)
	cor.mtest <- function(mat, method) {
		mat <- as.matrix(mat)
		n <- ncol(mat)
		p.mat <- matrix(NA, n, n)
		diag(p.mat) <- 0
		for (i in 1:(n - 1)) {
			for (j in (i + 1):n) {
		tmp <- cor.test(mat[, i], mat[, j], method = method)
		p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
		}
		}
		colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
		p.mat
		}
	p.mat <- cor.mtest(data, method = method)
	col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
	corrplot(mat,
		method = "color", col = col(200), number.font = number.font,
		mar = mar, number.cex = number.cex,
			type = type, order = order,
					addCoef.col = "black", # add correlation coefficient
					tl.col = "black", tl.srt = tl.srt, # rotation of text labels
			# combine with significance level
		p.mat = p.mat, sig.level = sig.level, insig = "blank",
			# hide correlation coefficiens on the diagonal
			diag = diag
		)
	}
			# Corrplot2
		corrplot2(
	data = ${1:mydf},
	method = "pearson",
	sig.level = 0.05,
	order = "original",
	diag = FALSE,
	type = "upper",
	tl.srt = 75
	)


snippet my_slice
	${1:mydf} %>% slice_sample(n=5)
	${1:mydf} %>% slice_min(${2:myvar}, prop=0.25)
	${1:mydf} %>% slice_max(${2:myvar}, n=5)

snippet my_externalR
	```{r setup, include=FALSE}
	knitr::opts_chunk$set(echo=FALSE, 
		warning=FALSE,
		message=FALSE,
		cache = FALSE,
		include = TRUE,
		# results = 'hide',
		error = TRUE)
	```
	```{r, include=FALSE, cache=FALSE}
			knitr::read_chunk('externalR.R')
	```
	```{r adelie-penguins}
	```
	## ---- adelie-penguins
		adelie <- penguins %>%
		filter(species=="Adelie", !is.na(body_mass_g))


snippet my_child
	```{r, echo=FALSE, warning=FALSE,message=FALSE, cache = FALSE, include = TRUE}
		library(tidyverse)
		library(palmerpenguins)
		# res <- knitr::knit_child('adelie-report.Rmd', quiet = FALSE)
		# cat(res, sep = '\n')
	```
	# child-chunk
	```{r test-main, child = 'adelie-report.Rmd', echo=FALSE} 
			# https://yihui.org/knitr/demo/child/  
	```  
	
snippet my_case_when  
```{r,  echo=FALSE, warning=FALSE,message=FALSE, cache = FALSE, include = TRUE}
	my_df %>%
	mutate(quarter = case_when(
		Month %in% c("Jan", "Feb", "Mar") ~ "Q1",
		Month %in% c("Apr", "May", "Jun") ~ "Q2",
		Month %in% c("Jul", "Aug", "Sep") ~ "Q3",
		Month %in% c("Oct", "Nov", "Dec") ~ "Q4",
		TRUE ~ "NA"
		))
```
snippet my_replace_values
		${1:mydf}$	${2:my_var}[	${1:mydf}$	${2:my_var}=="	${3:my_value_old}"] <-"	${4:my_value_new}"
			${1:mydf}$	${2:my_var}[	${1:mydf}$	${2:my_var} %in% c("${3:my_value_old}", "${4:my_value_old2}"] <-"	${5:my_value_new}"


snippet my_annotate_vline
	ggplot(data=${1:mydf}, aes(x=${2:myxcol}))+
	geom_histogram(fill="skyblue", alpha=0.5, binwidth = 0.25) +
	ggtitle("Count of Expiring Sections: Years to Expiration for 2,328 Section Prospect") +
	geom_vline(aes(xintercept = median(${2:myxcol})), col="red", size=1) +
	geom_vline(aes(xintercept = mean(${2:myxcol})), col="blue", size=1) +
	theme_minimal() +
	annotate("text", x = 4, y = 400,label= "Red = Median") +
	annotate("text", x = 4, y = 500,label= "Blue = Mean")  
	
snippet my_workbook  
	library(openxlsx)
	wb <- createWorkbook()
	addWorksheet(wb, "Sheet1")
	writeData(wb,"Sheet1", ${1:mydf})
	saveWorkbook(wb, "./data/myworkbook.xlsx", overwrite=TRUE) 
	
snippet my_kniter 
```{r setup, include=FALSE, echo=FALSE }
	knitr::opts_chunk$set( 
	echo = FALSE,
	message = FALSE,
	warning = FALSE) 
	options(scipen=999)
	if(!require("pacman")){
		install.packages("pacman")
	}
	pacman::p_load(DT, dplyr, ggplot2, tmap, scales, leaflet)	
```


snippet my_citation_yaml
---
title: "What is R?"
author: 
output:
	html_document:
	df_print: paged
	pdf_document: default
bibliography: "../MyLibrary.bib"
Link-citation: true

---


snippet my_round
	${1:mydf} %>%
		mutate_at(vars(c(${2:myvar1},${3:myvar2}, ${4:myvar3}, ${5:myvar4})), round, 2)  
		
snippet my_gttable
library(gt)
library(tidyverse)
library(glue)
	gt_tbl <- gt_tbl %>%
		tab_header(
		title = md("**Summary of Landman Acquisitions**"),
		subtitle = md("*RoyAc = Sum of NetAc * NRI*")
	) %>%
		data_color(
		columns = vars(Avg_Royalty),
		colors = scales::col_numeric(
			palette = c(
			"lightgreen", "red"),
			domain = c(NULL))
	)
	# Show the gt Table
	gt_tbl
	
snippet my_treemap
	library(treemapify)
	ggplot(df_roy, aes(area = TotalRoyAc,
					fill = initials,
					label = TotalRoyAc,
					subgroup = initials)) +
		geom_treemap() +
		geom_treemap_subgroup_border() +
		geom_treemap_subgroup_text(place = "centre",
								grow = F,
								alpha = 0.5,
								colour = "black",
								fontface = "italic",
								min.size = 0) +
		geom_treemap_text(colour = "white", place = "topleft", reflow = T) +
				labs(y = " ",
				x = NULL,
				title = "Who is Contributing the Greatest Number of Royalty Acres?",
				subtitle = "Royalty Acres = Sum of Roy Acres * NRI")

